---
title: "Additional regression analysis"
author: "Zezhen Wu"
date: "2023-08-16"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F)
```

**Note: The correlation between the predicted likelihood of being hired and the predicted performance score (average levels gain) among the current hired facilitators is 0.38. Please see "analysis/additional_cor_analysis.py" for detailed analysis.**

**Below we show exploratory results using application data to predict hiring/performance with the aim to interpret individual parameters, instead of model performance as in a supervised learning framework.**

# Load data
```{r}
# load data
library(tidyverse)
library(stargazer)

dat_hiring <- read_csv(here::here("myapp/data/application_all_mi.csv"))
dat_perform <- read_csv(here::here("myapp/data/application_hired_mi.csv"))

```

# Predicting hiring

Important parameters positively predicting more likelihood of being hired:

- Hired in T1 2022
- Hired in Kgatleng
- Returning applicant to Youth Impact
- Composite hiring score
- Younger applicant
- Having a Bachelor and above diploma
- Employment duration
- Less time working as a teacher, more time as a volunteer
- Interest with children
- Planning together with fellow facilitators when mentor does not show

```{r, results = "asis"}
logistic_hiring <- glm(
  yi_hired ~ .,
  family = "binomial",
  data = dat_hiring
)

stargazer(logistic_hiring, type = "html", title = "Predicting hiring decisions using application information")
```

# Predicting performance

Important parameters positively predicting better performance:

- Hired in T1 2022
- Hired in Central
- Composite hiring score
- Having a Bachelor and above diploma
- Having a Senior Secondary diploma
- Being employed
- **Less time working as a employee, less time as a volunteer (?)**
- **Less interest with children (?)**

```{r, results = "asis"}
lm_perform <- lm(
  level_gains ~ .,
  data = dat_perform
)

stargazer(lm_perform, type = "html", title = "Predicting average levels gained using application information")
```
